### 2017-04-26 thesis/latex/thesis.tex
Thesis: Add a bit of changes to Results.

\subsection{Exploring the parameter space}
Once validated, the model was fit to experimental data. Figure \ref{fig:kb-kub-heatmap} shows a heat map of the behavior of simulations running at many different $k_b$ and $k_{ub}$ values. The color of each point represents the fit quality of a simulation's $\left<t_{ob}\right>$ value to experiment. As can be seen, a good fit is found in the $k_b=XX$, $k_{ub}=YY$ region.

\subsection{Stepping behavior of fit model}
The ideal set of parameters found via the fitting process is shown in Table \ref{table:final-parameter-table}.\\

\begin{figure}[H]
  \centering
  \begin{tabular}{| l | l | l | l | l | l | l | l | l | l | l | l | l | l | l |}
    \hline
    $L_s$ & $L_t$ & $R_b$ & $R_m$ & $R_t$ & $\theta_{m}^{Pre}$ & $\theta_{m}^{Post}$ & $\theta_{b}$ & $\theta_{t}$ & $A_{ub}$ & $A_b$ & $c_t$ & $c_m$  &$c_b$\\ \hline
    21.0nm & 11.15nm & 1.45nm & 6.3nm & 2.2nm & 136$^{\circ}$ & 171$^{\circ}$ & 63.5$^{\circ}$ & 0$^{\circ}$ &  &  &  &   & \\ \hline
  \end{tabular}
  \caption{Ideal parameters for model stepping.}{Table of ideal parameters for reproducing \textit{in vivo} dynein stepping behavior.}
  \label{table:final-parameter-table}
\end{figure}

Histograms of the simulation's stepping length and time are shown in Figure \ref{fig:final-histograms}. This figure also shows histograms for experimental dynein stepping behavior.\\

@@

>>>>

\subsection{Model achieves processivity}
At certain input parameters, the model can successfully take steps. Figure \ref{fig:stepping-ghosts} shows snapshots of the model at various times throughout a simulation. The model steps back and forth, taking both forwards and backwards steps.\\

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../figures/stepping-ghosts}
  \caption{Snapshots of model over the course of a simulation. Bothbound states are depicted immediately after binding events. Onebound states depict the conformation with the highest unbound binding domain between binding events. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
  \label{fig:stepping-ghosts}
\end{figure}

More detailed stepping information is shown in Figure \ref{fig:stepping-trajectory}. The model steps both forwards and backwards, but has a definite forward bias.

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../figures/stepping-trajectory}
  \caption{Near and far binding domains over the course of a simulation. Simulation run at standard conditions with $k_b=123 s^{-1}, k_{ub}=456 s^{-1}, c_b=c_m=c_t=789 \Delta G_{ATP}$.}
  \label{fig:stepping-trajectory}
\end{figure}

--------------------------
Histograms of the simulation's stepping length and time are shown in Figure \ref{fig:final-histograms}. This figure also shows histograms for experimental dynein stepping behavior.\\

@@

\subsection{Current work: Refining model parameters}
Once validated, the model was fit to experimental data. Figure \ref{fig:kb-kub-heatmap} shows a heat map of the behavior of simulations running at many different $k_b$ and $k_{ub}$ values. The color of each point represents the fit quality of a simulation's $\left<t_{ob}\right>$ value to experiment. As can be seen, a good fit is found in the $k_b=XX$, $k_{ub}=YY$ region.
